Analytical Model for the Current Density in the Electrochemical Synthesis of Porous Silicon Structures with a Lateral Gradient

### 2020-11-17 paper.tex
Change abstract

\begin{document}
\shorttitle{Model for the ECh Sythesis of PS Structures with a Lateral Gradient}
\shortauthors{Ospina-Delacruz et al.}
\title[mode=title]{Model for the Electrochemical Synthesis of Porous
  Silicon Structures with a Lateral Gradient}
\author[1]{C. A. Ospina-Delacruz}[orcid=0000-0002-9609-3031]
\ead{crisalod@gmail.com}
\credit{Investigation; Software; Writing - original draft}
\author[1,2]{V. Agarwal}[orcid=0000-0003-2168-853X]
\fnmark[1]
\ead{vagarwal@uaem.mx}
\credit{Funding acquisition; Investigation; Supervision; Software; Writing - review \& editing}
\author[2]{W. L. Mochán}[type=editor,orcid=0000-0003-0418-5375]
\cormark[cor1]
\ead{mochan@fis.unam.mx}
\credit{Conceptualization; Funding acquisition; Investigation;
  Methodology; Supervision; Writing - review \& editing}
\address[1]{Centro de
  Investigación en Ingeniería y Ciencias Aplicadas (CIICAp-IICBA),
  Universidad Autónoma del Estado de Morelos (UAEM), Cuernavaca CP
  62209, México}
\address[2]{Instituto de Ciencias F\'isicas, Universidad Nacional
  Autonóma de México, Av. Universidad S/N, Col. Chamilpa, 62210
  Cuernavaca, Morelos, México}
\fntext[fn1]{On sabatical leave at ICF-UNAM from CIICAP-UAEM.}
\cortext[cor1]{Corresponding author}

\begin{keywords}
  Porous Silicon\sep GRIN \sep Reflectance Spectra.
\end{keywords}

\maketitle

\begin{abstract}
A variety of optical devices and applications may be based on layered
systems which have a lateral gradient in both their refractive indices
and their thicknesses. They may be fabricated of porous silicon (PS) through an
electrochemical process in which the etching current depends on position. Thus, the possibility of
predicting the local current density $j$ and the corresponding
porosity $p$ and etching rate $v$ would be desirable for a systematic design of these
structures. In this work, we propose a
simple model for the calculation of $j$
as a function of position within an electrochemical cell. We prepared
some graded single layer PS samples, measured their optical properties through
ultraviolet-visible-near infrared reflectance
spectroscopy, and related them
to their local porosity and thickness which, together with our model, were then used to obtain
the $p$ vs. $j$ and $v$ vs. $j$ calibration curves.  The dependence of
porosity and thickness with position was corroborated through scanning electron microscopy. We
compared the calibration curves for different samples. Thus, from
measurements on only one, or a few simple systems, we may obtain full
calibration curves which may be used to predict, design, and fabricate
more complex novel non-homogenous devices with lateral gradients which can be used
for manifold applications.
\end{abstract}

>>>>

\begin{document}
\shorttitle{Model of the Current Density in the Electrochemical
  Synthesis of PS Structures with a Lateral Gradient}
\shortauthors{Ospina-Delacruz et al.}
\title[mode=title]{Analytical Model for the Current Density in
the Electrochemical Synthesis of Porous Silicon Structures with a
Lateral Gradient}
\author[1]{C. A. Ospina-Delacruz}[orcid=0000-0002-9609-3031]
\ead{crisalod@gmail.com}
\credit{Investigation; Software; Writing - original draft}
\author[1,2]{V. Agarwal}[orcid=0000-0003-2168-853X]
\fnmark[1]
\ead{vagarwal@uaem.mx}
\credit{Funding acquisition; Investigation; Supervision; Software; Writing - review \& editing}
\author[2]{W. L. Mochán}[type=editor,orcid=0000-0003-0418-5375]
\cormark[1]
\ead{mochan@fis.unam.mx}
\credit{Conceptualization; Funding acquisition; Investigation;
  Methodology; Supervision; Writing - review \& editing}
\address[1]{Centro de
  Investigación en Ingeniería y Ciencias Aplicadas (CIICAp-IICBA),
  Universidad Autónoma del Estado de Morelos (UAEM), Cuernavaca CP
  62209, México}
\address[2]{Instituto de Ciencias F\'isicas, Universidad Nacional
  Autonóma de México, Av. Universidad S/N, Col. Chamilpa, 62210
  Cuernavaca, Morelos, México}
\fntext[fn1]{On sabatical leave at ICF-UNAM from CIICAP-UAEM.}
\cortext[cor1]{Corresponding author}
\begin{keywords}
  Porous Silicon\sep GRIN \sep Reflectance Spectra.\sep
\end{keywords}
\maketitle
\begin{abstract}
  A variety of optical devices and applications are based on
  layered systems which have a lateral gradient in both their
  refractive indices and their thicknesses. Simple fabrication of such
  systems can be carried out through the electrochemical synthesis of
  porous silicon (PS) using an etching current with a density $\bm
  j(\bm r_\|)$ that has a spatial variation along the surface of the
  sample. Thus, the possibility of predicting the local
  value of $\bm j(\bm r_\|)$ and the corresponding values of the porosity
  $p(\bm r_\|)$ and the etching rate $v(\bm r_\|)$ is desirable for a
  systematic design of these structures.
  In this work, we propose a simple analytical model based on a simple
  fast converging planewise summation of Coulomb potentials in two
  dimensional reciprocal space for the
  calculation of $\bm j(\bm r_\|)$ as a function of position
  within a prism shaped electrochemical cell. Some graded single layer PS samples
  were synthesized and their optical reflectance were used to
  estimate their local porosity $p(\bm r_\|)$ and thickness $d(\bm r_\|)$
  which, together with our model, were then used to obtain the basic
  calibration curves $p$ vs $\bm j$ and $v$ vs $\bm j$.
  The dependence of porosity and thickness with position was
  corroborated through scanning electron microscopy.
  Agreement was found between the calibration curves from
  different samples. Thus, from measurements on only one system, full
  calibration curves may be obtained and used to predict, design, and
  fabricate more complex novel non-homogenous multilayered devices with lateral
  gradients which can be used for manifold applications.

\end{abstract}
